Split-Apply-Combine with Dynamic Grouping

### 2024-05-17 paper/jss5097.Rnw
.

%% - \author{} with primary affiliation (and optionally ORCID link)
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Mark P.J. van der Loo~\orcidlink{0000-0002-9807-4686}\\
        Statistics Netherlands and University of Leiden}

@@

%% - \Keywords{} with LaTeX markup, at least one required
%% - \Plainkeywords{} without LaTeX markup (if necessary)
%% - Should be comma-separated and in sentence case.
\Keywords{data analysis, \proglang{R}}
\Plainkeywords{data analysis, R}

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Mark P.J. van der Loo~\orcidlink{0000-0002-9807-4686}\\
  Research and Development\\
  Statistics Netherlands\\
  Henri Faasdreef 312\\
  2492JP Den Haag, the Netherlands\\
  E-mail: \email{mpj.vanderloo@cbs.nl}\\
  URL: \url{https://www.markvanderloo.eu}\\
  \emph{and}\\
  Leiden Institute of Advanced Computer Science (LIACS)\\
  University of Leiden\\
  P.O. Box 9512\\
  2300 RA Leiden, The Netherlands\\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliography{refs}

>>>>

%% - \author{} with primary affiliation (and optionally ORCID link)
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Mark P.J. van der Loo~\orcidlink{0000-0002-9807-4686}\\
        Statistics Netherlands and Leiden University}

@@

%% - \Keywords{} with LaTeX markup, at least one required
%% - \Plainkeywords{} without LaTeX markup (if necessary)
%% - Should be comma-separated and in sentence case.
\Keywords{data analysis, estimation, aggregation, \proglang{R}}
\Plainkeywords{data analysis, R}

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Mark P.J. van der Loo~\orcidlink{0000-0002-9807-4686}\\
  Research and Development\\
  Statistics Netherlands\\
  Henri Faasdreef 312\\
  2492JP Den Haag, the Netherlands\\
  E-mail: \email{mpj.vanderloo@cbs.nl}\\
  URL: \url{https://www.markvanderloo.eu}\\
  \emph{and}\\
  Leiden Institute of Advanced Computer Science (LIACS)\\
  Leiden University\\
  P.O. Box 9512\\
  2300 RA Leiden, The Netherlands\\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliography{jss5097}
